Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-10-15 doc/framework.tex
fleshed out framework

\section{Introduction}
\todo{Phil,(+ Tom)}{Update introduction to reflect the scope of this paper}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Theoretical Background}
\label{sec:theory}
\todo{Phil,(+ Tom)}{Modify the current theory section, emphasiszing how $\kappax$ effects inferred parameters. Justify how we combine individual $\kappa$s to give a total $kappah$ - note that this is the weak lensing limit.}

@@

\section{Estimating external convergence: The halo model approximation}
\label{sec:model}

@@

\subsection{Calibration: Recovering the global $\pr(\kappax)$ using a void correction}
\label{subsec:voids}

\todo{tom}{Outline _EXPLICITLY_ the proceedure we use to correct for voids etc}

@@

\section{Testing the halo model approximation with known halo mass and redshift}
\label{sec:knownMh+z}

\subsection{How does $\kappah$ relate to $\kappax$?}
Done?
\subsubsection{How does $\gammah$ relate to $\gammax$?}
\todo{tom}{do}
\subsection{Does converting from $\kappah$ to $\kappax$ work?}
\todo{tom}{do}

\subsection{Where does $\kappah$ come from?}
\todo{tom}{do}
\subsubsection{Magnitude}
\subsubsection{Distance}
\subsubsection{Redshift}

\section{Applying the Halo Model approximation to mock catalogs}
\label{sec:obsMstar+z}
\todo{tom}{redo - using new Mhalo-Mstar code}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

>>>>

\section{Introduction}
\todo{Phil,(+ Tom)}{Update introduction to reflect the scope of this paper}

Every distant object we observe has had its shape distorted, and size
and total brightness magnified (or demagnified) by a compound lens constructed
from all the mass distributed between us and it. As \citet{valewhite2003} and \citet{hilbert}
showed, there are no empty lightcones in our universe. This fact makes gravitational lensing a potentially important source of systematic error for any estimate of luminosity or distance.

\citet{suyu} found that in time delay lens cosmography the
lensing effect of mass structures along the (unusually over-dense) line of
sight to the quadruply-imaged radio source B1608$+$656, the so-called ``external
convergence'' $\kappax$, was the dominant source of uncertainty in the inferred
cosmological parameters. The problem is that one simply doesn't know
how magnified and distorted the source has been because the unlensed source is unobservable. The external shear can potentially be recovered in the mass-modelling of the lens, but the convergence is undetectable from the image positions, shapes and relative fluxes; this is the famous {\emph{  mass sheet-degeneracy}} \citep[see e.g.][for details]{falco}.

\notes{Previous work, what we are doing, why it will help}

@@

\section{Theoretical Background}
\label{sec:theory}
\todo{Phil,(+ Tom)}{Modify the current theory section}

\notes{what is $\kappa$ from a single object, how does it combine given lots of objects along the line of sight, why kappa can't be extracted - mass sheet degeneracy, how $\kappa$ effects inferred parameters}

\section{Estimating external convergence: The halo model approximation}
\label{sec:model}
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\notes{given perfect knowledge of the density near a line of sight it is possible to raytrace, but this can't be done for a real line of sight, since the mass distribution isn't known. Galaxies are known due to their light. Need to infer z and $\Mstar$ and turn these into $\Mh$ which can be used to infer $\kappah$ for each halo. Will never know voids, filaments or other dark structures, so a calibration is needed to convert $\kappah$ into $\kappa$}

\notes{halo profile; justfication, choice of truncation. Infer concentration from halo mass using a relation.}

\subsection{Correcting for voids, filaments and dark structures}
\label{subsec:voids}

\notes{Outline EXPLICITLY the proceedure we use to correct for voids etc}

\section{Using the Millenium Simulation to test the halo model approximation with known halo mass and redshift}
\label{sec:knownMh+z}

In order to justify the reconstruction proceedure outlined in Section \ref{sec:model}, we would like to apply it to lines of sight with known $\kappa$.\notes{can't use real los, have to use \MS}

@@

\notes{view of a lightcone figure should go at the end of this section}
\subsection{How does $\kappah$ relate to $\kappa$?}
Given the halo mass catalogue from the Millenium Simulation, 
and convergence maps produced by ray-tracing through the MS's n-body particles, 
it is possible to test the validity of the prescription outlined
 in Section \ref{sec:model}. We test the model by comparing $\kappah$ against
 the ray-traced $\kappa$. If the reconstruction process is to be
 succesfull the two quantities should be closely related, although we expect $\kappah$ to be offset from $\kappa$ since the former does not include the divergence due to voids.

\subsubsection{How does $\gammah$ relate to $\gamma$?}

\subsection{How succesful is the calibration at converting $\kappah$ into $\kappa$?}

\subsection{Which halos dominate the $\kappah$ distribution?}
\subsubsection{Magnitude}
\subsubsection{Distance}
\subsubsection{Redshift}

@@

\section{Applying the Halo Model approximation to mock catalogs}
\label{sec:obsMstar+z}
\todo{tom}{redo - using new Mhalo-Mstar code}

\subsubsection{Reconstructing $\kappa$ given a spectroscopic redshift for every object}

\subsubsection{Reconstructing $\kappa$ from photometry alone}

\subsubsection{Reconstructing $\kappa$ with a }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Improving precision by including additional information}
\notes{placeholder for shear}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
